---
title: "Sweet Potato Biscuits & Gravy"
author: "Adam Spannbauer"
date: "4/9/2017"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
```

```{r}
library(tidyverse)

ingredients_b <- data_frame(
  Dish       = "biscuit",
  Ingredient = c("all purpose flour",
                 "baking powder",
                 "granulated sugar",
                 "salt",
                 "baking soda",
                 "whole milk",
                 "sweet potato",
                 "unsalted butter",
                 "heavy cream"),
  Amount = c(2,1,1,.5,.25,.75,1,8,1),
  Unit   = c("cup(s)","tbs","tbs","tsp","tsp","cup(s)","cup(s)","tbs","tbs"),
  Notes  = c(NA,NA,NA,NA,NA,NA,
             "1 medium sweet potato",
             "1 stick frozen",
             "just enough to brush tops")
)
ingredients_g <- data_frame(
  Dish       = "gravy",
  Ingredient = c("sausage",
                 "unsalted butter",
                 "all purpose flour",
                 "maple syrup",
                 "black pepper",
                 "whole milk",
                 "heavy cream"),
  Amount = c(.5,2,2,2,2,.75,2),
  Unit   = c("lbs","tbs","tbs","tbs","tsp","cup(s)","tbs"),
  Notes  = c(NA,NA,NA,NA,NA,NA,NA)
)
ingredients_all <- bind_rows(ingredients_b,
                             ingredients_g) %>% 
  group_by(Ingredient, Unit) %>% 
  summarise(Amount = sum(Amount)) %>% 
  ungroup() %>% 
  arrange(Unit) %>% 
  group_by(Ingredient) %>% 
  summarise(Amount = paste(format(Amount), collapse=" + "),
            Unit = paste(Unit, collapse=" / ")) %>% 
  select(Ingredient, Amount, Unit) %>% 
  arrange(Unit)
```

# Sweet Potato Biscuits & Gravy

* [Ingredients](#ingredients)
* [Instructions](#instructions)

## I. Ingredients
### Biscuits
```{r}
ingredients_b %>% 
  select(-Dish) %>% 
  mutate(Amount = format(Amount)) %>% 
  mutate(Notes  = ifelse(is.na(Notes), "", Notes)) %>% 
  knitr::kable(align = c("l","r","l","l"))
```

### Gravy
```{r}
ingredients_g %>% 
  select(-Dish) %>% 
  mutate(Amount = format(Amount)) %>% 
  mutate(Notes  = ifelse(is.na(Notes), "", Notes)) %>% 
  knitr::kable(align = c("l","r","l","l"))
```

### Total
```{r}
knitr::kable(ingredients_all,
             align = c("l","r","l"))
```

## II. Instructions
### Biscuits
1. Preheat oven to 400°F
2. Combine 2 cups flour, 1 tbs baking powder, 1 tbs sugar, .5 tsp salt, & .25 tsp baking soda in large mixing bowl and set aside
3. In separate large bowl, mix together .75 cups whole milk & mashed sweet potato until evenly combined
4. Grate 1 stick frozen butter through large holes of box grater and toss with dry ingredients until butter is coated
5. Add milk mixture to dry ingredients and mix lightly until dough forms a shaggy mass
6. Turn out mixture onto floured surface and knead just until it comes together (~30 sec)
7. Roll out dough to about 3/4 inch thick
8. Using 3 inch biscuit cutter or glass cut dough into rounds
9. Place biscuits on baking sheet
10. Brush tops with heavy cream
11. Bake until bottoms are golden brown (12-15 min)

### Gravy
1. Brown sausage over medium heat
2. Pour off grease
3. Add 2 tbs of butter to pan and stir until melted
4. Sprinkle in 2 tbs of flour and cook, stirring constantly for 1 minute, being careful not to brown the flour
5. Add 2 tbs maple syrup and 2 tsp pepper
6. Slowly pour 3/4 cups whole milk into pan stirring constantly as gravy thickens
7. Add 2 tbs heavy cream to thickened gravy and mix well
8. Add salt & pepper to taste (usually don't need it)
